A weakly structured stem for human origins in Africa

### 2022-08-05 paper.tex
Typo fix and add cites

Other studies have fit tree-like demographic models to African populations
using distributions of allele frequencies or related statistics, finding
inconsistent divergence times, some of which older than the ones we find here
\cite{Henn2018-rf,Bergstrom2021-iw}. In Section~\ref{sec:IM-reinfer} , we show that this discrepancy
can be explained by model misspecification: if divergence is estimated using an isolation with migration (IM) model
with constant population sizes, but the correct model has ancient population growth or population structure,
the inferred IM models have split times that are much deeper than in the correct model.

>>>>

Other studies have fit tree-like demographic models to African populations
using distributions of allele frequencies or related statistics, finding
inconsistent divergence times, some of which older than the ones we find here
\cite{Henn2018-rf,Bergstrom2021-iw}. In Section~\ref{sec:IM-reinfer}, we show that this discrepancy
can be explained by model misspecification: if divergence is estimated using an isolation with migration (IM) model
with constant population sizes, but the correct model has ancient population growth or population structure,
the inferred IM models have split times that are much deeper than in the correct model \citep{Momigliano2021-th,Shchur2022-wa}.
